%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Content of this file is not licensed:
% Copyright (c) 2020 Stefano Tribioli
%
% Based on a template licensed under:
% The MIT License (see included LICENSE_TEMPLATE.md file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[9pt]{developercv}

\begin{document}

\begin{minipage}[t]{0.42\textwidth}
	\vspace{-\baselineskip}
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Stefano}}}}}
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Tribioli}}}}}
\end{minipage}
\begin{minipage}[t]{0.29\textwidth}
	\vspace{-\baselineskip}
	
	\icon{MapMarker}{12}{Milan, Italy}\\
	\icon{At}{12}{tribioli.stefano@gmail.com}\\	
\end{minipage}
\begin{minipage}[t]{0.29\textwidth}
	\vspace{-\baselineskip}
	
	\icon{Globe}{12}{\href{https://tribioli.it}{tribioli.it}}\\
	\icon{Github}{12}{\href{https://github.com/sassospicco}{github.com/sassospicco}}\\
	\\
\end{minipage}

\begin{minipage}[t]{1\textwidth}
\vspace{6pt}
\LARGE Cloud and Infrastructure Manager at Accenture
\end{minipage}

\cvsect{In brief}

\begin{minipage}[t]{1\textwidth}
	\vspace{-\baselineskip}
	System engineer from Italy.
	\\
	I joined Accenture in 2015 and I have since been working in Cloud and Security projects for large enterprise clients.
\end{minipage}

\cvsect{Jobs}

\begin{entrylist}
	\entry
		{Dec 2020 -- present}
		{Cloud and Infrastructure Manager}
		{Accenture}
		{Milan, Italy}
		{
			I have been responsible for sales and delivery of Cloud and Infrastructure projects undertaken by Accenture at two major Italian telcos, leading a team ranging from 5 to 15 people, depending on our workload.
			\\
			I have been managing projects worth around 600 k€ of annual revenues and I have been personally involved in the sale of about half of them.
			\\
			\\
			The main project I followed in 2021 was the design and development of a security system to monitor and protect a CRM processing personal data of tens of millions of customers.
			\\
			The goal was to detect and block insider threats (fraud and data exfiltration), analyzing the behavioral patterns of agents.
			The system consisted of a custom Go module and a Redis cluster, for real-time decisions. Custom Python scripts and a MySQL database were used for historical analytics. A Layer7 API Gateway handled the production traffic.
			\\
			\\
			In 2022, I have mainly been following the Cloud migration for a telco. The company is parting ways with its former parent and we are migrating all its AWS servers to a new AWS org on a different region, re-wiring connections and dependencies as we go.
		}
	\entry
		{Oct 2018 -- Nov 2020}
		{IT Operations Team Lead}
		{Accenture}
		{Rome, Italy}
		{
			I led a seven-person team in charge of deploying and operating the e-commerce back-end for a major Italian telco. The system processed purchases for one of the top three Italian mobile apps.
			\\
			My team developed the CI/CD pipeline (orchestrated by Jenkins and with OpenShift as the main target) and followed system operations, ensuring availability and continuously refining monitoring and reporting tools (based on the Elastic stack, with custom Python and Bash scripts).
		}
	\entry
		{Jun 2017 -- Sep 2018}
		{Cloud Automation Consultant}
		{Accenture}
		{Paris, France}
		{
			Working for a major insurance group in Paris, I followed as PMO a key transformation project to adopt Automation solutions in an hybrid cloud environment.
			\\
			Our scope encompassed all branches in Europe, across six nations, and covered the analysis and design phases.
		}
	\entry
		{Feb 2015 -- May 2017}
		{Application Security Analyst}
		{Accenture}
		{Rome, Italy}
		{
			Working at a major Italian telco, I followed Security-related activities for one of the largest digital transformation project ever run by Accenture in Europe.
			\\
			I designed and implemented solutions to secure data flows, integrate systems with IAM services, and restrict access to web APIs.
			\\
			The project mainly revolved around enterprise middleware products, like Oracle Fusion Middleware and Tibco BusinessWorks, and the CA/Layer7 API Gateway product.
		}
	\entry
		{Dec 2010 -- Dec 2015}
		{Farming entrepreneur}
		{Tribiolio}
		{Scandriglia, Italy}
		{
			In order to earn an income during my university years, I started a small business for olive oil production. I cultivated an hectare of olive trees and sold around 150 liters per year.
		}
\end{entrylist}

\cvsect{Education}

\begin{entrylist}
	\entry
		{Nov 2012 -- Jan 2015}
		{Master’s Degree -- Telecommunications Engineering}
		{Sapienza Università di Roma}
		{Rome, Italy}
		{
			Grade: 110 cum laude/110
			\\
			Thesis: \textit{Developing an Hypervisor for Lightweight Virtualization of OpenLISP Routers}.
		}
	%\entry
		\parbox[t]{0.2\textwidth}{
			Feb 2014 -- Jul 2014
		}
		&\parbox[t]{0.8\textwidth}{
			\textbf{Erasmus Period} at \textbf{TU Delft}
			\\
			\textcolor{lightgrey}{Delft, Netherlands}
		}\\\\
	\entry
		{Sep 2009 -- Nov 2012}
		{Bachelor’s Degree -- Aerospace Engineering}
		{Sapienza Università di Roma}
		{Rome, Italy}
		{
			Grade: 110 cum laude/110
			\\
			Thesis: \textit{Delay- and Disruption-Tolerant Networking for Deep Space Communications: a Survey}.
		}
	\entry
		{Nov 2004 -- Jul 2009}
		{Scientific diploma}
		{Augusto Righi lyceum}
		{Rome, Italy}
		{Grade: 100/100}
\end{entrylist}

\cvsect{Coding}

\begin{minipage}[t]{1\textwidth}
	\vspace{-\baselineskip}
	I can develop fairly complex projects in Java or Go and simpler programs in Bash, Python, JavaScript, Dart, C, or MATLAB.
	\\
	I am at ease working with different operating systems and their tools: I have been working as a GNU/Linux sysadmin and I did FreeBSD kernel programming in academia.
\end{minipage}

\cvsect{Certifications}

\begin{entrylist}
	\entryCert
		{Jun 2020}
		{GCP Associate Cloud Engineer}
		{Google Cloud}
	\entryCert
		{Jul 2017}
		{AWS Certified Solutions Architect -- Associate}
		{AWS}
	\entryCert
		{Jul 2016}
		{ISO/IEC 27001 Lead Auditor}
		{BSI Group}
	\entryCert
		{May 2013}
		{TOEFL iBT (108/120)}
		{ETS}
\end{entrylist}

\begin{minipage}[t]{1\textwidth}
	\vspace{-\baselineskip}

	\cvsect{Languages}
	
	\textbf{Italian} -- native\\
	\textbf{English} -- proficient
\end{minipage}

\end{document}
